Foundational claims of group polarization are plausibly false, with lessons for the empirical study of psychological dynamics

### 2024-05-02 GroupPolarizationStatmod/paper/ms.qmd
paper updates

\paragraph{Atheoretical} The first of ten studies we included in our meta-analysis was by Moscovici and Zavalloni (1969) [@Moscovici1969] who sought to measure group polarization among groups of French high school students who discussed domestic and foreign politics. Moscovici and Zavalloni tested four conditions whether group polarization occurred for two different questions and two different rating systems: participants were asked their opinions on then-president Charles De Gaulle and their opinion about foreign aid from the USA either in the "Opinion" setting or the "Judgement" condition (see Table 4 on p. 132).

@@

\paragraph{Social comparisons} In developing the social comparisons theory of group polarization (described in Myers (1978) [@Myers1978]), Myers and Bishop (1970), writing in *Science,* [@Myers1970] sought to measure group polarization among high school students in the United States who discussed racial attitudes and Myers (1975) [@Myers1975] measured group polarization in groups of college students discussing the quality of a faculty member in one condition, and women's rights and issues in another condition.

@@

The ten studies we included each tested several experimental conditions meant to elicit group polarization in novel experimental groups, 60 in total, which we briefly introduce here. \

>>>>

\paragraph{Atheoretical}

The first of ten studies we included in our meta-analysis was by Moscovici and Zavalloni (1969) [@Moscovici1969] who sought to measure group polarization among groups of French high school students who discussed domestic and foreign politics. Moscovici and Zavalloni tested four conditions whether group polarization occurred for two different questions and two different rating systems: participants were asked their opinions on then-president Charles De Gaulle and their opinion about foreign aid from the USA either in the "Opinion" setting or the "Judgement" condition (see Table 4 on p. 132).

@@

\paragraph{Social comparisons}

In developing the social comparisons theory of group polarization (described in Myers (1978) [@Myers1978]), Myers and Bishop (1970), writing in *Science,* [@Myers1970] sought to measure group polarization among high school students in the United States who discussed racial attitudes and Myers (1975) [@Myers1975] measured group polarization in groups of college students discussing the quality of a faculty member in one condition, and women's rights and issues in another condition.

@@

The ten studies we included each tested several experimental conditions meant to elicit group polarization in novel experimental groups, 60 in total, which we briefly introduce here.\
